Ontology Matching with word2vec

### 2016-03-07 Paper/Draft.tex
Small changes to the draft
Restored part of the lost draft

 \section{Introduction}

 \section{Problem}
 \subsection{Short Context}
 On the Semantic Web, ontologies are used to define and share knowledge.
 \subsection{Problem}
 When knowledge bases are combined, their ontologies need to be merged.
 \subsection{Research questions}

@@

  %  Ja doe maar een ander voorbeeld ivm gelijkheid e.d.\endcomment

@@

  %  Goeie woord?\endcomment

@@

  % Check spelling\endcomment

@@

  % Moet voorafgaand stukje op een andere plek?\endcomment

@@

  % Dit moet weg als het bs blijkt te zijn\endcomment

@@

  % Herschrijf dit aub want het is niet goed\endcomment

>>>>

 \section{Introduction}
 % Voorbeeld van semantisch web

 \section{Problem}
 \subsection{Short Context}
 On the Semantic Web, ontologies are used to define and share knowledge. The term ontology will be properly defined later on, but for now it suffices to know that an ontology is a set of rules that determine what relations are allowed and required. On the semantic web, ontologies are the foundation for communication between agents.

 However, on the Semantic Web it is infeasible to use one single ontology, since the number of concepts it would have to contain is incredibly large. The larger an ontology the longer it takes to perform inference and searches on it, and thus to longer it takes to use it for communication. Therefore the semantic web will have separate ontologies for every domain. The downside of this approach is that when communication requires rules on multiple domains, which it often does, multiple ontologies need to be aligned or merged.
 \subsection{Problem}
 We have seen that when information from multiple domains need to be integrated so that it is possible to reason over them together, the ontologies of those domains need to be aligned or merged. Those ontologies contain rules about concepts and concept classes in the shape of triplets, with two concepts and a relation. For example, the rule{\tt Professors are humans} contains the concepts \emph{Professor} and \emph{human} and relationship \emph{being}.

 If we want to merge two ontologies, we need to find the concepts from the different ontologies that are related by an 'is-same-as' or other rule.

 However, since the ontologies are made for different domains, the same concept can be represented by different labels in the two ontologies. This problem is called the synonymy problem, as synonyms are two words that refer to the same concepts.

 The opposite problem is called the homonymy problem, in which two concepts are represented by the same label. Since they have the same label, naive algorithms might align the concepts as being the same, when they are not.

 Then there is the problem of ambiguity, which encompasses many other problems. It encompasses the fact that some concepts are used wrongly by humans, but also the fact that some concepts are extremely similar, and may occur in the same context, but are still slightly different.

 Lastly, there is the problem of 
 \subsection{Research questions}

@@

  %  Ja doe maar een ander voorbeeld ivm gelijkheid e.d.

@@

  %  Goeie woord?

@@

  % Check spelling

@@

  % Moet voorafgaand stukje op een andere plek?

@@

  % Dit moet weg als het bs blijkt te zijn

@@

  % Herschrijf dit aub want het is niet goed
